\subsection{Functional Requirements that were not implemented}

We were not able to implement all our functional requirements, the reasons
being lack of time. The features which were dropped rely heavily on
content-production and would require quite some time to polish and balance in
terms of gameplay.

The architecture itself could handle these additions with
little work, but we simply didn't have the time to add these features.
No amount of planning could have detected this problem, and we feel there
was little in the architecture process which would account for such problems.

Below is a list of the features which were not implemented, along with a short
description of what we wished to achieve, and the reason it was left out.


\begin{table}[H]
	\resizebox{\textwidth}{!}{
	\rowcolors{0}{white}{tableShade}
	\begin{tabular}{p{5cm} | p{12cm}}
    	\hline
		\textbf{ID:} 			& 	\textbf{FR10} \\ 
		\hline
    	
		\textbf{Priority:}		&	High \\
		\textbf{Description}	& 	A hero / player has a limited amount of 
		                            resources \\ 
		\textbf{Rationale}		& 	The game is cooperative, and adding depth 
		                            to the game \\
		\hline
		\textbf{Exclusion rationale} & Time, architecture supports adding this 
		                               feature easily. \\
    \end{tabular}
	\label{tab:functional10}}
\end{table}

Resources were intended as a bonus, in order to allow players to grow stronger
as the game progressed. In a sense we did this by adding a leveling mechanism,
but this was already a separate requirement. We had envisioned the resources
as metal / credits which were dropped by hostiles as they died, and used by
the player to purchase upgraded equipment from a store.

We realized soon that implementing this feature would be simple, but creating
art assets and balancing the stats of each item would require much more time
than we had available. Due to this the feature was scrapped quite early in the
implementation.

\begin{table}[H]
	\resizebox{\textwidth}{!}{
	\rowcolors{0}{white}{tableShade}
	\begin{tabular}{p{5cm} | p{12cm}}
    	\hline
		\textbf{ID:} 			& 	\textbf{FR16} \\
		\hline
		\textbf{Priority:}		&	Low	\\
		\textbf{Description}	& 	A hero can buy items to enhance abilities 
		                            or skills \\ 
		\textbf{Rationale}		& 	The game is cooperative \\
		\hline
		\textbf{Exclusion rationale} & Relies heavily on resources. So removed 
		                               due to FR10 \\
    \end{tabular}
	\label{tab:functional16}}
\end{table}

This requirement is a natural extension of \emph{FR10}, and when that was 
dropped this requirement has to be dropped alongside it.

\begin{table}[H]
	\resizebox{\textwidth}{!}{
	\rowcolors{0}{white}{tableShade}
	\begin{tabular}{p{5cm} | p{12cm}}
    	\hline
		\textbf{ID:} 			& 	\textbf{FR18} \\ 
		\hline
		\textbf{Priority:}		&	Medium \\
		\textbf{Description}	& 	Passive abilities does not need to be 
		                            activated by the player	\\ 
		\textbf{Rationale}		& 	According to the conceptual model of this 
		                            genre of games \\
		\hline
	    \textbf{Exclusion rationale} & 	We have only added active abilities. \\
 	\end{tabular}
	\label{tab:functional18}}
\end{table}

Passive abilities would be of the kind \emph{Increase teams health 
regeneration} or \emph{Reduce hostiles damage resistance}.  These effects can
be added with the current architecture as abilities which can always be 
triggered (i.e. without cooldowns).

This feature was scrapped due to time-constraints, but would require very 
little change to code to be implemented. Once again we were reaching too high
for a project running over four weeks.
