The game is built from the ground up to be played on the XBOX 360, but
has limited playability on Windows-based PCs.  An XBOX controller is
required to play this game.

We only distribute the source for this game, and as such the installation
procedure is somewhat complex, and has many prerequisites.

\subsection{Installing the game}

To play on PC:
\begin{itemize}
    \item Ensure both Visual Studio 2010 and XNA Game Studio 4.0 are installed
    \item Open the solution \emph{progark-spill} in VS.
    \item Build the solution (Key shortcut F6)
    \item Run without debugging (Key shortcut Ctrl+F5)
\end{itemize}

To play on XBOX 360:
\begin{itemize}
    \item Follow the first three steps for PC.
    \item Download and install \emph{XNA Creators Club} on your XBOX.
    \item Launch XNA-CC on your XBOX, and pair with development machine.
    \item When XNA-CC is awaiting a connection, choose \emph{Deploy} in
          VS.
    \item Finally, choose Run without debugging in VS.
    \item The game is now installed, and on following launches should
          be found in the XBOX' Game Library.
\end{itemize}

\subsection{Playing the game}

In the game, you should now see the main menu. It lists all connected 
controllers, and thus potential players. Each player that wishes to join the
game, must press the button \emph{A} on their controller. When you are ready,
press \emph{Start} on player ones' controller to launch the game.  You may quit 
the game from this menu by pressing the \emph{Back} button.  This
description has unfortunately not been added to the menu itself, due to
time-constraints.

% TODO:  Add ingame shot for context?
You should now be playing the game. At any time you should be able to press
the \emph{Back} button to return to the main-menu, or \emph{Start} button to
pause the game. Pressing \emph{Back} when the game is paused returns you to
the game.

In the center of the screen you should see the objective, which you must 
defend. You should also see a spaceship for each player which joined the game.
You control your spaceship with the \emph{Left Stick} of your controller.
The spaceship always faces the crosshair, which you can move around using
your \emph{Right Stick}. You can shoot using your \emph{Right trigger}.

Along the top of your screen you should see a bar, representing the time
left of this level. When it reaches zero, and all enemies have been destroyed
you win the level (and in the case of the demo-level, the game itself).
Should the objective be destroyed, you lose the game.

On the right edge of the screen you can see which abilities you may use.
This UI element records the time until you can use an ability, by filling
pieces of a pie-chart. The pies are color-coded to buttons on your controller.
A white ring surrounding the pies means you have leveled up, and can improve
one of your abilities.You do this by pressing the corresponding direction
on you \emph{D-Pad}